PropOcData2

### 2021-09-06 R/PropOc Data 3D.Rmd

PlotPropOcAllMeanSD <- function(relation) {
  plot1<- ggplot()+
    geom_linerange(data=combinedData %>% filter(Relation ==relation), 
                   aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Strain, linetype =factor(BioRep), group = Experiment),
                   position = position_dodge(width =.8), size=.7)+
    facet_wrap(~Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy mean +/- SD"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,".png"),plot = plot1, width = 20, height = 10)
}
PlotPropOcAllMeanSD("Pa->Pa")
PlotPropOcAllMeanSD("Pa->Sa")
PlotPropOcAllMeanSD("Sa->Sa")
PlotPropOcAllMeanSD("Sa->Pa")
```
Another metric used is the coefficient of variation, CV, which is the ratio of the standard deviation to the mean.So, let's also visualize that.
```{r Plot CV} 
PlotCVrelation <- function(relation){
  plot1<-ggplot()+ 
    geom_point(data=combinedData %>% filter(Relation =="Pa->Pa"), 
               aes(x=Distance,y = CV, color = Strain, shape = factor(BioRep), group = Experiment),
               position = position_dodge(width =.8), size=4)+
    geom_hline(yintercept = 1, linetype = "dashed")+
    facet_wrap( ~ Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy Coefficient of variation (SD/mean)"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+ 
    theme(plot.title = element_text(hjust = 0.5)) 
  ggsave(paste0(relation,"-CV.eps"),plot = plot1, width = 20, height = 10)
  ggsave(paste0(relation,"-CV.png"),plot = plot1, width = 20, height = 10)
  }
PlotCVrelation("Pa->Pa")
PlotCVrelation("Pa->Sa")
PlotCVrelation("Sa->Sa")
PlotCVrelation("Sa->Pa")
```
Importing whole data sets to identify distribution of data
the chunk below is the only one aplicable to the SaPa chronic wounds project, all the other ones are just for reference

```{r read whole data sets}
ReadPropOcFile<-function(file){
    propOcData<-read.csv(file,header = T)
    fileName<-str_split(basename(file), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
    print(paste0("Importing sample ", fileName))
    attrList<-str_split(fileName,"_")[[1]]
    propOcData<-propOcData %>% mutate(Condition = attrList[1], TimePoint = attrList[2], Replicate = attrList[3], SampleCode = fileName)
    return(propOcData)
    }

@@

  PlotMaxDensities <- function(sample) {
  ggplot()+
    geom_jitter(data = propOcMaxDensity %>% filter(Sample ==sample),aes(x=Value, y=Density,color = Distance),size=2)+
    labs(title ="Maximum Density")+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMaxDensities("pqsL_d4_03")
#####
#maximum distribution isn't super representative, so for the distribution, I calculated the value at which 50% of the population is found

@@

PropOcDataFiltered1<-PropOcDataFiltered %>% group_by(Condition,TimePoint,SampleCode) %>% summarise(None = n()) %>% mutate(Sample = SampleCode)

propOcMidDensitylabeled <-merge(propOcMidDensity,PropOcDataFiltered1)

@@

propOcMidDensityStats<-propOcMidDensitylabeled %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint, Distance, Relation) %>% summarize(meanValue = mean(Value), sdValue = sd(Value), medianValue = median(Value))

ggplot()+
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=meanValue, x = Distance,color=Condition, shape = "Mean"),size=2)+
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
    labs(title ="mean 50 percentile Density")+
    facet_grid(Relation ~ TimePoint)+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

ggplot()+#Pa->Pa
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=meanValue, x = Distance,color=Culture, shape = "Mean"),size=2)+
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=medianValue, x = Distance,color=Culture,shape = "Median"),size=2)+
    labs(title ="mean 50 percentile Density")+
    facet_grid(Strain ~ TimePoint)+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

@@

PlotMedianEnrichment50percent<-function(df1,df2){
  ggplot()+
    geom_pointrange(data = df1,aes(y=medianED,ymax=per25,ymin=per75, x = Condition,shape = Region),position = position_dodge(width = .5),size = .7)+
  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition),width = .5, height = 0,size=1, shape = 1)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
    #facet_grid(.~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
}
PlotMedianEnrichment50percent(pOEnrMetaStatsRegion %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
#then without region
PlotMedianEnrichment50percentNRegion<-function(df1,df2){
  ggplot()+
    geom_pointrange(data = df1,aes(y=medianED,ymax=per25,ymin=per75, x = Condition),size = .7)+
  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition),width = .2, height = 0,size=1, shape = 1)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
    #facet_grid(.~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
}
PlotMeanEnrichment50percentNRegion<-function(df1,df2){
  ggplot()+
    geom_pointrange(data = df1,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, x = Condition),size = .7)+
  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition, group = Region),width = .2, height = 0,size=1, shape = 1)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
    #facet_grid(.~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
}
PlotMeanEnrichment50percentNRegion(pOEnrMetaStats %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
PlotMedianEnrichment50percentNRegion(pOEnrMetaStats %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))

@@

ggplot()+
    geom_pointrange(data = pOEnrMetaStatsRegion,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, shape = Region,x = Condition),
                    position = position_dodge(width = .5))+
    geom_point(data = pOEnrMetaClean,aes(y=WmeanDist,x = Condition, group = Region),position = position_dodge(width = .5),size=1, shape = 1)+
    labs(y = expression("Enrichment distance ("*mu*"m)")) +
    facet_grid(TimePoint~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12,margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
    panel_border()

@@

#Enrichment (distance at highest proportional occupancy) 
```{r Enrichment}
#find the max proportional occupancy value from the 50 percentile

>>>>

PlotPropOcAllMeanSD <- function(relation) {
  plot1<- ggplot()+
    geom_linerange(data=combinedData %>% filter(Relation ==relation), 
                   aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Strain, linetype =factor(BioRep), group = Experiment),
                   position = position_dodge(width =.8), size=.7)+
    facet_wrap(~Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy mean +/- SD"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,".png"),plot = plot1, width = 20, height = 10)
}
PlotPropOcAllMeanSD("Pa->Pa")
PlotPropOcAllMeanSD("Pa->Sa")
PlotPropOcAllMeanSD("Sa->Sa")
PlotPropOcAllMeanSD("Sa->Pa")
```
Another metric used is the coefficient of variation, CV, which is the ratio of the standard deviation to the mean.So, let's also visualize that.
```{r Plot CV} 
PlotCVrelation <- function(relation){
  plot1<-ggplot()+ 
    geom_point(data=combinedData %>% filter(Relation =="Pa->Pa"), 
               aes(x=Distance,y = CV, color = Strain, shape = factor(BioRep), group = Experiment),
               position = position_dodge(width =.8), size=4)+
    geom_hline(yintercept = 1, linetype = "dashed")+
    facet_wrap( ~ Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy Coefficient of variation (SD/mean)"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+ 
    theme(plot.title = element_text(hjust = 0.5)) 
  ggsave(paste0(relation,"-CV.eps"),plot = plot1, width = 20, height = 10)
  ggsave(paste0(relation,"-CV.png"),plot = plot1, width = 20, height = 10)
  }
PlotCVrelation("Pa->Pa")
PlotCVrelation("Pa->Sa")
PlotCVrelation("Sa->Sa")
PlotCVrelation("Sa->Pa")
```

The chunk below is the only one aplicable to the SaPa chronic wounds project, all the other ones are just for reference

```{r SAPA Chorinc wounds paper chunk}
ReadPropOcFile<-function(file){
    propOcData<-read.csv(file,header = T)
    fileName<-str_split(basename(file), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
    print(paste0("Importing sample ", fileName))
    attrList<-str_split(fileName,"_")[[1]]
    propOcData<-propOcData %>% mutate(Condition = attrList[1], TimePoint = attrList[2], Replicate = attrList[3], SampleCode = fileName)
    return(propOcData)
    }

@@

  PlotMaxDensities <- function(sample) {
  ggplot()+
    geom_jitter(data = propOcMaxDensity %>% filter(Sample ==sample),aes(x=Value, y=Density,color = Distance),size=2)+
    labs(title ="Maximum Density")+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMaxDensities("pqsL_d4_03")
#####
#maximum frequency isn't super representative, so for the distribution, I calculated the value at which 50% of the population is found

@@

PropOcDataFiltered1<-PropOcDataFiltered %>% group_by(Condition,TimePoint,Region,SampleCode) %>% summarise(None = n()) %>% mutate(Sample = SampleCode)

propOcMidDensitylabeled <-merge(propOcMidDensity,PropOcDataFiltered1)#Add condition and timepoint

@@

#add region
metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
metaData.df$SampleCode<-as.factor(metaData.df$SampleCode)
metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)#
propOcMidDensMetaLabel<-metaData.df %>%  merge(propOcMidDensitylabeled, by = "SampleCode")

#include Region
propOcMidDensityStatsRegion<-propOcMidDensMetaLabel %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint,Region, Distance, Relation) %>% summarize(meanValue = mean(Value), sdValue = std.error(Value), medianValue = median(Value))
#exclude region
propOcMidDensityStats<-propOcMidDensMetaLabel %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint,Distance, Relation) %>% summarize(meanValue = mean(Value), sdValue = std.error(Value), medianValue = median(Value))

PlotMeanMidDensityPORegion<-function(relation){
  ggplot()+
    geom_pointrange(data = propOcMidDensityStatsRegion %>% filter(TimePoint == "Day 4", Relation== relation),aes(y=meanValue,ymin= meanValue-(sdValue/2), ymax = meanValue+(sdValue/2), x = Distance,color=Condition, shape = Region),size=1, position = position_dodge(width = .6))+
    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title ="mean 50 percentile Density")+
    facet_grid(Relation ~ .)+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
#Including Edge
PlotMeanMidDensityPORegion("Pa->Sa")
PlotMeanMidDensityPORegion("Sa->Pa")#this is log exponential
PlotMeanMidDensityPORegion("Pa->Pa")
PlotMeanMidDensityPORegion("Sa->Sa")

PlotMeanMidDensityPO<-function(relation){
  ggplot()+
    geom_pointrange(data = propOcMidDensityStats %>% filter(TimePoint == "Day 4", Relation== relation),aes(y=meanValue,ymin= meanValue-(sdValue/2), ymax = meanValue+(sdValue/2), x = Distance,color=Condition),size=1, position = position_dodge(width = .6))+
    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title ="mean 50 percentile Density")+
    facet_grid(Relation ~ .)+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMeanMidDensityPO("Pa->Sa")
PlotMeanMidDensityPO("Sa->Pa")#this is log exponential
PlotMeanMidDensityPO("Pa->Pa")
PlotMeanMidDensityPO("Sa->Sa")
#this wat combines the data accroding to the focus species
PlotMeanMidDensityPOCenter<-function(){
  ggplot()+
    geom_pointrange(data = propOcMidDensityStats %>% filter(TimePoint == "Day 4", Culture == "co") %>% filter(Relation%in%c("Sa->Sa","Sa->Pa")),
    #geom_pointrange(data = propOcMidDensityStats %>% filter(TimePoint == "Day 4", Culture == "co") %>% filter(Relation%in%c("Pa->Sa","Pa->Pa")),
                      aes(y=meanValue,ymin= meanValue-(sdValue/2), ymax = meanValue+(sdValue/2), x = Distance,color=Relation),size=1, position = position_dodge(width = .6))+
    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title ="mean 50 percentile Density")+
    facet_grid(.~Condition )+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMeanMidDensityPOCenter()
PlotMeanMidDensityPOCenterRegion<-function(){
  ggplot()+
    #geom_pointrange(data = propOcMidDensityStatsRegion %>% filter(TimePoint == "Day 4", Culture == "co") %>% filter(Relation%in%c("Sa->Sa","Sa->Pa")),
    geom_pointrange(data = propOcMidDensityStatsRegion %>% filter(TimePoint == "Day 4", Culture == "co") %>% filter(Relation%in%c("Pa->Sa","Pa->Pa")),
                      aes(y=meanValue,ymin= meanValue-(sdValue/2), ymax = meanValue+(sdValue/2), x = Distance,shape = Region,color=Relation),
    size=1, position = position_dodge(width = .6))+
    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title ="mean 50 percentile Density")+
    facet_grid(.~Condition )+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMeanMidDensityPOCenterRegion()
#Calculate empty space

emptySpaceRgn<-propOcMidDensityStatsRegion %>% mutate(Focus = recode(Relation, "Pa->Sa" = "Pa","Pa->Pa" = "Pa","Sa->Sa" = "Sa","Sa->Pa" = "Sa")) %>% group_by(Focus, Distance, Condition, TimePoint, Region) %>% mutate(EmptySpace = 1-(sum(meanValue)), SDEmptySpace = sum(sdValue))

emptySpace<-propOcMidDensityStats %>% mutate(Focus = recode(Relation, "Pa->Sa" = "Pa","Pa->Pa" = "Pa","Sa->Sa" = "Sa","Sa->Pa" = "Sa")) %>% group_by(Focus, Distance, Condition, TimePoint) %>% mutate(EmptySpace = 1-(sum(meanValue)), SDEmptySpace = sum(sdValue))
PlotEmptySpace<-function(focus){
  ggplot()+
    geom_pointrange(data = emptySpace %>% filter(TimePoint == "Day 4", Focus== focus),aes(y=EmptySpace,ymin= EmptySpace-(SDEmptySpace/2), ymax = EmptySpace+(SDEmptySpace/2), x = Distance,color=Strain),size=1, position = position_dodge(width = .6))+
    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title ="mean 50 percentile Density")+
    facet_grid( .~Culture)+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotEmptySpace("Pa")
PlotEmptySpace("Sa")

PlotEmptySpaceRegion<-function(focus){
  ggplot()+
    geom_pointrange(data = emptySpaceRgn %>% filter(TimePoint == "Day 4", Focus== focus),
                    aes(y=EmptySpace,ymin= EmptySpace-(SDEmptySpace/2), ymax = EmptySpace+(SDEmptySpace/2), x = Distance,color=Strain, shape = Region),size=1, position = position_dodge(width = .6))+
    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title ="mean 50 percentile Density")+
    facet_grid( .~Culture)+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotEmptySpaceRegion("Pa")
PlotEmptySpaceRegion("Sa")

@@

PlotMedianEnrichment50percent<-function(df1,df2){
  ggplot()+
    geom_pointrange(data = df1,aes(y=medianED,ymax=per25,ymin=per75, x = Condition,shape = Region),position = position_dodge(width = .5),size = .7)+
  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition),width = .5, height = 0,size=1, shape = 1)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
    #facet_grid(.~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
}
PlotMedianEnrichment50percent(pOEnrMetaStatsRegion %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
#then without region
PlotMedianEnrichment50percentNRegion<-function(df1,df2){
  ggplot()+
    geom_pointrange(data = df1,aes(y=medianED,ymax=per25,ymin=per75, x = Condition),size = .7)+
  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition),width = .2, height = 0,size=1, shape = 1)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
    #facet_grid(.~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
}
PlotMeanEnrichment50percentNRegion<-function(df1,df2){
  ggplot()+
    geom_pointrange(data = df1,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, x = Condition),size = .7)+
  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition, group = Region),width = .2, height = 0,size=1, shape = 1)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
    #facet_grid(.~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
}

PlotMeanEnrichment50percentNRegion(pOEnrMetaStats %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
PlotMedianEnrichment50percentNRegion(pOEnrMetaStats %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))

@@

ggplot()+
    geom_pointrange(data = pOEnrMetaStatsRegion,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, shape = Region,x = Condition),
                    position = position_dodge(width = .5))+
    geom_point(data = pOEnrMetaClean,aes(y=WmeanDist,x = Condition, group = Region),position = position_dodge(width = .5),size=1, shape = 1)+
    labs(y = expression("Enrichment distance ("*mu*"m)")) +
    facet_grid(TimePoint~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12,margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
    panel_border() 
```

@@

#Enrichment (distance at highest proportional occupancy) 
```{r Enrichment -DONE}
#find the max proportional occupancy value from the 50 percentile
